% vim: tw=80 sw=2 ts=2 ff=unix spelllang=en spell
\input{include/beamer-header}
\title{DATeCH 2017 -- \pocoto{} Workshop -- Introduction}
\author{Florian~Fink \& Uwe~Springmann}
%% {
%% 	Florian~Fink \href{mailto:finkf@cis.lmu.de}{finkf@cis.lmu.de}\\
%% 	Uwe~Springmann
%% 	\href{mailto:uwe.springmann@uni-wuerzburg.de}{uwe.springmann@uni-wuerzburg.de}
%% }

\begin{document}

\begin{frame}
	\titlepage
\end{frame}

\section{Introduction}
\subsection{Schedule}
\begin{frame}
	\begin{itemize}
		\item 13:00 - 13:15: Introduction
		\item 13:15 - 14:00: \pocoto{}
		\item 14:00 - 15:00: Hands on \pocoto{}
		\item 15:00 - 16:00: Profiler
		\item 16:00 - 17:00: Hands on Profiler
		\item There will be time between the sessions for short coffee breaks!
	\end{itemize}
\end{frame}

\subsection{Overview}
\begin{frame}
	This Workshop covers two main topics:
	\begin{enumerate}
		\item The \pocoto{} PostCorrectionTool: A tool to do interactive
			postcorrection of OCR'ed (historical) documents.
		\item The language Profiler: A tool that enables error detection and error
			correction for historical documents.
	\end{enumerate}
\end{frame}

\subsection{\pocoto{} and the profiler}
\begin{frame}
	\begin{itemize}
		\item \pocoto{} and the language profiler are independent from each other.
		\item You can use \pocoto{} for interactive correction of OCR'ed documents.
		\item You can use the profiler for error detection and error correction.
		\item \pocoto{} can work together with the profiler to detect errors and
			error pattern and to use correction suggestions.
	\end{itemize}
\end{frame}

\subsection{Resources}
\begin{frame}
	\begin{itemize}
		\item The USB stick, that you received at the registration contains a data
			file \texttt{datech-2017-workshop-pocoto.zip} (\texttt{DATeCH 2017 -
			Goettingen/Preconference-workshops/PoCoTo})
		\item There is a github repository, that contains a lot more data related to
			historical OCR and our developed tools (including slides of this and other
			workshops and the sources of the profiler and \pocoto{}):
			\href{https://github.com/cisocrgroup}{\url{https://github.com/cisocrgroup}}
	\end{itemize}
\end{frame}

\subsection{Workshop data file}
\begin{frame}
	The data file contains data to be used in this workshop:
	\begin{itemize}
		\item The \pocoto{}-manual
		\item The profiler-manual
		\item A OCR-project of \emph{Die Grenzboten, 1844} (ABBYY)
		\item A OCR-project of \emph{Heiligenleben, 1488} (Ocropus)
		\item A binary version of \pocoto{}
	\end{itemize}
\end{frame}

\section{}
\subsection{}
\begin{frame}
	\centering{
		\Huge Thanks for your attention!
	}
\end{frame}

\end{document}
